Proportional multi-state multiple-cohort life table model

### 2018-03-29 MSLT/MSLTdoc.Rmd
Creating inputs table

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing
output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in
  bibliography: MSLT\Bibliography.txt
---

@@

```{r}
inputs <- matrix(c("Life table", "Synthetic population", "", "Life table", "Synthetic population", "", "Life table", "GBD Results tool (http://ghdx.healthdata.org/gbd-results-tool)","", "Disease life table", "GBD Results tool (http://ghdx.healthdata.org/gbd-results-tool) and Dismod II", "", "Disease life table", "GBD Results tool (http://ghdx.healthdata.org/gbd-results-tool) and Dismod II", "", "", "Disease life table", "GBD Results tool (http://ghdx.healthdata.org/gbd-results-tool)"),ncol= 3,byrow=TRUE)
colnames(inputs) <- c("Life table/Disease life table","","")
rownames(inputs) <- c("Population","All-cause mortality", "Total YLD rates", "Incidence", "Case fatality", "Disability weighs")
inputs <- as.table(inputs)
inputs
```

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

>>>>

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing
output:
  pdf_document: 
    toc: true
    number_sections: true
    fig_caption: yes
  fontsize: 12 pt
  geometry: margin=1in

---

@@

```{r, echo=FALSE}
inputs <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18)
colnames(inputs) <- c("Life table","Source","Comments")
rownames(inputs) <- c("Population", "All-cause mortality", "Total YLD rate", "Incidence", "Case fatality", "Disability weight")
inputs <- as.table(inputs)
inputs
```
